Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-10-02 Article.tex
Update bibliography

The raw stress-strain data is exported from the Gleeble thermomechanical simulator as true stress and true strain, and the set of 30 flow stress curves $\sigma$ versus strain $\varepsilon$ obtained from compression tests for each test condition is reported in Figure \ref{fig:RawData}.
All strain/stress data is composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in \textcolor{purple}{$0.001$} increments.
\begin{figure}[H]
\centering
\includegraphics[width=0.9\columnwidth]{Figures/rawData}
\caption{Stress--strain curves of medium carbon alloy extracted from the Gleeble device for 5 temperatures ($T$) and 6 strain rates ($\mdot\varepsilon$).}
\label{fig:RawData}
\end{figure}

@@

To improve the results obtained through the process of identifying critical values, we suggest employing the universal approximator capability of artificial neural networks.
This \textcolor{purple}{can be done by characterizing} each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
In this type of network, each layer of neurons is linked to the preceding and subsequent layers through weighted connections.
Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following~equation:
\begin{equation}
y_i\lay{k} = \sum_{j=1}^m w_{ij}\lay{k} \hat{y}_j^{(k-1)}+ b_i\lay{k},\label{eq:ANN1}
\end{equation}
where $y_i\lay{k}$ is the entry of the $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the $i$th neuron of layer $k$ and the $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the $i$th neuron of layer $k$.
Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN, which we have to adjust during the training procedure.
For the proposed model, we selected the Sigmoid activation function, so that each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
\begin{equation}
\hat{y}=\frac{1}{1 + \e{-y}}\label{eq:ANN2}
\end{equation}

@@

In general terms, flow stress $\sigma$ is a non-linear function of the strain $\varepsilon$, increasing with the strain rate $\mdot\varepsilon$, but decreasing with increasing temperature $T$.
This model can be described as an elastoplastic model that takes into consideration the influence of temperature and strain rate.
This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978}, PTM \textcolor{purple}{\cite{TizeMha-2023}} or Arrhenius \cite{Sellars-1966} flow law type.
Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.

>>>>

The raw stress-strain data is exported from the Gleeble thermomechanical simulator as true stress and true strain, and the set of 30 flow stress curves $\sigma$ versus strain $\varepsilon$ obtained from compression tests for each test condition is reported in Figure \ref{fig:RawData}.
All strain/stress data is composed of 701 equidistant strain values from $\varepsilon=0.0$ to $\varepsilon=0.7$ in $0.01$ increments.
\begin{figure}[H]
\centering
\includegraphics[width=0.9\columnwidth]{Figures/rawData}
\caption{Stress--strain curves of medium carbon alloy extracted from the Gleeble device for 5 temperatures ($T$) and 6 strain rates ($\mdot\varepsilon$).}
\label{fig:RawData}
\end{figure}

@@

To improve the results obtained through the process of identifying critical values, we suggest employing the universal approximator capability of artificial neural networks.
This can be Done ! by characterizing each strain-hardening curve using an ANN with just one input (strain) and one output (stress).
In this type of network, each layer of neurons is linked to the preceding and subsequent layers through weighted connections.
Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following~equation:
\begin{equation}
y_i\lay{k} = \sum_{j=1}^m w_{ij}\lay{k} \hat{y}_j^{(k-1)}+ b_i\lay{k},\label{eq:ANN1}
\end{equation}
where $y_i\lay{k}$ is the entry of the $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the $i$th neuron of layer $k$ and the $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the $i$th neuron of layer $k$.
Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN, which we have to adjust during the training procedure.
For the proposed model, we selected the Sigmoid activation function, so that each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
\begin{equation}
\hat{y}=\frac{1}{1 + \e{-y}}\label{eq:ANN2}
\end{equation}

@@

In general terms, flow stress $\sigma$ is a non-linear function of the strain $\varepsilon$, increasing with the strain rate $\mdot\varepsilon$, but decreasing with increasing temperature $T$.
This model can be described as an elastoplastic model that takes into consideration the influence of temperature and strain rate.
This type of behavior generally leads to Johnson--Cook \cite{Johnson-1983}, Zerilli--Armstrong \cite{Zerilli-1987}, Hansel--Spittel \cite{Hensel-1978}, PTM \cite{mha2022generalized} or Arrhenius \cite{Sellars-1966} flow law type.
Depending on the nature of the stress-strain relationship, modeling with one or other of these models can take into account the actual behavior of the material at certain strain rates.
